### 2017-12-24 article.tex
change from "scrreprt" to "scrartcl"

\chapter{Dividends}
\section{Factors on Dividend Policy}
There are several factors that influence whether a company pays a dividend and how much it chooses to pay. Some of the most influential factors are listed as follows.
\begin{itemize}
	\item \textbf{Income stability.} 
	Income stability is one of the top factors in determining dividend policies. Specifically, established companies with stable, predictable income streams are more likely to pay dividends than companies with growing or volatile income.\\
	Newer and rapidly growing companies rarely pay dividends, as they prefer to invest their profits back into the company to fuel even more future growth. And, companies with unstable revenue streams often choose not to pay dividends, or pay small dividends in order to make sure the payout will be sustainable.\\
	It looks terrible to investors when companies are forced to suspend or reduce dividend payments, so most like to err on the side of caution when deciding to implement a new dividend, waiting for several years of stable profits before doing so.

@@

\section{Dividend Policy performed by JD.com}
JD.com, Inc. does not reflect an active attitudes towards dividend payment. So far JD.com have not declared or paid any dividends on ordinary shares, nor do JD.com have any present plan to pay any cash dividends on ordinary shares in the foreseeable future\footnote{JD.com, Inc. annual report 2016, Page 131}.

\chapter{Share Capital and Reserves}

@@

\chapter{Current Assets and Current Liabilities}
\section{Current Assets}
A current asset is any asset which can reasonably be expected to be sold, consumed, or exhausted through the normal operations of a business within the current fiscal year. JD.com records 11 current assets accounts in its consolidated balance Sheet\footnote{JD.com, Inc. annual report 2016, Page F-3}.

@@

\section{Current Liabilities}

@@

\section{Working Capital}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Working capital&9,485,092&2,191,863\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Working capital (In thousands of RMB \textyen)}\label{table:1}
\end{table}

\section{Current Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Current ratio&1.194&1.021\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current ratio}\label{table:1}
\end{table}

\section{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&29,819,341&4,391,955\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}

\chapter{Inventories}
\section{Inventory Values}

@@

\section{Inventory Valuation Policy}
Inventories, consisting of products available for sale, are stated at the lower of cost or market value\footnote{JD.com, Inc. annual report 2016, Page F-20}. Cost of inventory is determined using the weighted
average cost method. Adjustments are recorded to write down the cost of inventory to the estimated market value due to slow-moving merchandise and
damaged goods, which is dependent upon factors such as historical and forecasted consumer demand, and promotional environment. The Group takes
ownership, risks and rewards of the products purchased, but has arrangements to return unsold goods with certain vendors. Write downs are recorded in cost of
revenues in the Consolidated Statements of Operations and Comprehensive Loss.

The Group also provides fulfillment-related services in connection with the Group’s online marketplace. Third-party sellers maintain ownership of their
inventories and therefore these products are not included in the Group’s inventories.
\section{Gross Profit Percentage on Sale}

@@

\section{Inventory Turnover}
Based on the data of JD.com, Inc. consolidated balance sheet\footnote{JD.com, Inc. annual report 2016, Page F-3 and JD.com, Inc. annual report 2015, Page F-3} and consolidated statements of operations and comprehensive loss\footnote{JD.com, Inc. annual report 2016, Page F-48}, gross profit percentage on sale can be calculated as follows:

@@

\chapter{Example Chapter}

This is my text with an example Figure~\ref{fig:example} and example
citation~\cite{StrunkWhite} or \textcite{Bringhurst1993}. And there is another
\enquote{citation} which is located at the bottom\footcite{tagstore}.

\myfig{TU_Graz_Logo}%% filename in figures folder
  {width=0.1\textwidth,height=0.1\textheight}%% maximum width/height, aspect ratio will be kept
  {Example figure.}%% caption
  {}%% optional (short) caption for table of figures
  {fig:example}%% label

Now you are able to write your own document. Always keep in mind: it's
the \emph{content} that matters, not the form. But good typography is
able to deliver the content much better than information set with bad
typography. This template allows you to focus on writing good content
while the form is done by the template definitions.

>>>>

\section{Dividends}
\subsection{Factors on Dividend Policy}
There are several factors that influence whether a company pays a dividend and how much it chooses to pay. Some of the most influential factors are listed as follows.
\begin{itemize}
	\item \textbf{Income stability.} 
	Income stability is one of the top factors in determining dividend policies. Specifically, established companies with stable, predictable income streams are more likely to pay dividends than companies with growing or volatile income.\\
	Newer and rapidly growing companies rarely pay dividends, as they prefer to invest their profits back into the company to fuel even more future growth. And, companies with unstable revenue streams often choose not to pay dividends, or pay small dividends in order to make sure the payout will be sustainable.\\
	It looks terrible to investors when companies are forced to suspend or reduce dividend payments, so most like to err on the side of caution when deciding to implement a new dividend, waiting for several years of stable profits before doing so.

@@

\subsection{Dividend Policy performed by JD.com}
JD.com, Inc. does not reflect an active attitudes towards dividend payment. So far JD.com have not declared or paid any dividends on ordinary shares, nor do JD.com have any present plan to pay any cash dividends on ordinary shares in the foreseeable future\footnote{JD.com, Inc. annual report 2016, Page 131}.

\section{Share Capital and Reserves}

@@

\section{Current Assets and Current Liabilities}
\subsection{Current Assets}
A current asset is any asset which can reasonably be expected to be sold, consumed, or exhausted through the normal operations of a business within the current fiscal year. JD.com records 11 current assets accounts in its consolidated balance Sheet\footnote{JD.com, Inc. annual report 2016, Page F-3}.

@@

\subsection{Current Liabilities}

@@

\subsection{Working Capital}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Working capital&9,485,092&2,191,863\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Working capital (In thousands of RMB \textyen)}\label{table:1}
\end{table}

\subsection{Current Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Current ratio&1.194&1.021\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Current ratio}\label{table:1}
\end{table}

\subsection{Quick Ratio}
\begin{table}[H]	
	\begin{center}
		\begin{tabular}{lrr}
			\toprule
			\textbf{Fiscal year}&\textbf{2015}&\textbf{2016}\\
			\midrule
			Quick ratio&29,819,341&4,391,955\\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Quick ratio}\label{table:1}
\end{table}

\section{Inventories}
\subsection{Inventory Values}

@@

\subsection{Inventory Valuation Policy}
Inventories, consisting of products available for sale, are stated at the lower of cost or market value\footnote{JD.com, Inc. annual report 2016, Page F-20}. Cost of inventory is determined using the weighted
average cost method. Adjustments are recorded to write down the cost of inventory to the estimated market value due to slow-moving merchandise and
damaged goods, which is dependent upon factors such as historical and forecasted consumer demand, and promotional environment. The Group takes
ownership, risks and rewards of the products purchased, but has arrangements to return unsold goods with certain vendors. Write downs are recorded in cost of
revenues in the Consolidated Statements of Operations and Comprehensive Loss.

The Group also provides fulfillment-related services in connection with the Group’s online marketplace. Third-party sellers maintain ownership of their
inventories and therefore these products are not included in the Group’s inventories.
\subsection{Gross Profit Percentage on Sale}

@@

\subsection{Inventory Turnover}
Based on the data of JD.com, Inc. consolidated balance sheet\footnote{JD.com, Inc. annual report 2016, Page F-3 and JD.com, Inc. annual report 2015, Page F-3} and consolidated statements of operations and comprehensive loss\footnote{JD.com, Inc. annual report 2016, Page F-48}, gross profit percentage on sale can be calculated as follows:

@@

\newpage

\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
yu

%\section{Example Chapter}
%
%This is my text with an example Figure~\ref{fig:example} and example
%citation~\cite{StrunkWhite} or \textcite{Bringhurst1993}. And there is another
%\enquote{citation} which is located at the bottom\footcite{tagstore}.
%
%\myfig{TU_Graz_Logo}%% filename in figures folder
%  {width=0.1\textwidth,height=0.1\textheight}%% maximum width/height, aspect ratio will be kept
%  {Example figure.}%% caption
%  {}%% optional (short) caption for table of figures
%  {fig:example}%% label
%
%Now you are able to write your own document. Always keep in mind: it's
%the \emph{content} that matters, not the form. But good typography is
%able to deliver the content much better than information set with bad
%typography. This template allows you to focus on writing good content
%while the form is done by the template definitions.
